Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-10 intro.tex
ideal -> appropriate

To explore the relationship between complexity, predictive structure,
and predictability, we generate forecasts of a number of time-series
datasets using four different prediction methods, then compare the
accuracy of those predictions to the permutation entropy of the
associated signals.  This results in two primary findings:
\begin{enumerate}
\item The complexity of a noisy real-valued time series is
  quantifiable by permutation entropy and correlated with prediction
  accuracy of an ideal predictor [[we don't know that.  we only tried
      four methods.]]
\item The way information is generated and processed internally by a
  system plays a crucial role in the success of different forecasting
  schema.
\end{enumerate}
The forecast methods used here were chosen to span the space of
standard prediction strategies, but they do not cover that space
exhaustively.  Our goal here is an empirical assessment of the
relationship between predictability and complexity, not formal results
about a ``best'' predictor for a given time series.  From a
practitioner's standpoint, it would be useful to know {\sl a priori}
if a trace contains enough predictive structure to make it worth
spending the time and effort searching for a good forecast method.  It
would also be useful to know if a given method is inadequate---that
is, if one could do better and should keep searching.

>>>>

To explore the relationship between complexity, predictive structure,
and predictability, we generate forecasts of a number of time-series
datasets using four different prediction methods, then compare the
accuracy of those predictions to the permutation entropy of the
associated signals.  This results in two primary findings:
\begin{enumerate}
\item The complexity of a noisy real-valued time series is
  quantifiable by permutation entropy and correlated with prediction
  accuracy of an appropriate predictor.
\item The way information is generated and processed internally by a
  system plays a crucial role in the success of different forecasting
  schema, and in the choice of which forcasting scheme is appropriate.
\end{enumerate}
The forecast methods used here were chosen to span the space of
standard prediction strategies, but they do not cover that space
exhaustively.  Our goal here is an empirical assessment of the
relationship between predictability and complexity, not formal results
about a ``best'' predictor for a given time series.  From a
practitioner's standpoint, it would be useful to know {\sl a priori}
if a trace contains enough predictive structure to make it worth
spending the time and effort searching for a good forecast method.  It
would also be useful to know if a given method is inadequate---that
is, if one could do better and should keep searching.
